Dependently Typed Multi-stage Calculus

### 2019-11-30 slides/main.tex
fix.

@@

\begin{frame}[fragile]{What is Multi-stage Programming}
    A programming paradigm that enables
    \begin{itemize}
        \item Generation of code at run-time
        \item Evaluation of code at run-time
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using run-time information \\
            (a.k.a. run-time specialization)
        \item DSLs
    \end{itemize}
    \note{
        So, what is multi-stage programming? It is a programming paradigm that
        enables generation of code at run-time and evaluation of code at
        run-time simultaneously. Famous applications of multi-stage programming
        is speeding up programs using run-time information, which is also known
        as run-time specialization and DSLs, such as DSL for linear algebra or
        image processing.
    }
\end{frame}

@@

 # (run vadd3) [1;2] [4;5]
 [1;2] has type vec 2
 but was expected of type vec 3
 \end{Verbatim}
    \end{exampleblock}
    \note{
        Our approach to the problem is using dependent types. Dependent types
        are types dependent on values and can prevent illegal value of vadd3.
        Using dependent types, we can express the length of vectors in their
        types. For example, a vector [1;2] can be typed as vec 2 and vadd3 can
        be typed code of function which takes values of vec 3 type and return a
        value of vec 3 type. Now, if I apply wrong length vectors, [1;2] and
        [4;5] to vadd3, I get only type error not run-time error.
    }
\end{frame}

@@

\begin{frame}[fragile]{Kinding rules of \LMD}
    Kiding judgements also include stages.
    \begin{center}
        \( \G \vdash \tau :: K @ n \)
    \end{center}
    Because types may contains terms. (e.g. vec n)
    \begin{center}
        {\footnotesize
        \infrule[{\KApp}]{
            \G\V \sigma:: (\Pi x:\tau.K) @ n \andalso \G\V M:\tau @ n
        }{
            \G\V \sigma\ M::K[x\mapsto M] @ n
        } \\[2mm]
        \infrule[{\KAbs}]{
            \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@n
        }{
            \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
        }}
    \end{center}
    \note{
        Kiding judgements also include stages. Because types may contains terms
        such as vec n. It is natural that types dependent on a value live in
        the same stage of the value. So, application rule, K-App, says that if
        you want to apply term M to type sigma, they must live in the same
        stage n. K-Abs says when sigma is kinded at stage n and variable x in
        the environment is on stage n also, you can abstract x using Pi.
    }
\end{frame}

>>>>

\begin{frame}{}
\end{frame}

@@

\begin{frame}[fragile]{What is Multi-stage Programming?}
    A programming paradigm that enables
    \begin{itemize}
        \item Generation of code at run-time
        \item Evaluation of code at run-time
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using run-time information \\
            (a.k.a. run-time specialization)
        \item DSLs
    \end{itemize}
    \note{
        So, what is multi-stage programming? It is a programming paradigm that
        enables generation of code at run-time and evaluation of code at
        run-time simultaneously. Famous applications of multi-stage programming
        is speeding up programs using run-time information, which is also known
        as run-time specialization and DSLs, such as DSL for linear algebra or
        image processing.
    }
\end{frame}

@@

 # (run vadd3) [1;2] [4;5]
 [1;2] has type vec 2
 but a value of type Vec 3 was expected
 \end{Verbatim}
    \end{exampleblock}
    \note{
        Our approach to the problem is using dependent types. Dependent types
        are types dependent on values and can prevent illegal value of vadd3.
        Using dependent types, we can express the length of vectors in their
        types. For example, a vector [1;2] can be typed as vec 2 and vadd3 can
        be typed code of function which takes values of vec 3 type and return a
        value of vec 3 type. Now, if I apply wrong length vectors, [1;2] and
        [4;5] to vadd3, I get only type error not run-time error.
    }
\end{frame}

@@

\begin{frame}[fragile]{Kinding rules of \LMD}
    Kiding judgements as well include stages.
    \begin{center}
        \( \G \vdash \tau :: K @ n \)
    \end{center}
    Because types may contains terms. (e.g. vec n)
    \begin{center}
        {\footnotesize
        \infrule[{\KApp}]{
            \G\V \sigma:: (\Pi x:\tau.K) @ n \andalso \G\V M:\tau @ n
        }{
            \G\V \sigma\ M::K[x\mapsto M] @ n
        } \\[2mm]
        \infrule[{\KAbs}]{
            \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@n
        }{
            \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
        }}
    \end{center}
    \note{
        Kiding judgements also include stages. Because types may contains terms
        such as vec n. It is natural that types dependent on a value live in
        the same stage of the value. So, application rule, K-App, says that if
        you want to apply term M to type sigma, they must live in the same
        stage n. K-Abs says when sigma is kinded at stage n and variable x in
        the environment is on stage n also, you can abstract x using Pi.
    }
\end{frame}
